Preregistration: Estimating the Parameter Recovery of the Hidden Markov Model in gazeHMM

### 2020-05-19 simulation/preregistration/preregistration_parameter_recovery.Rmd
fix typos

For each parameter, we will calculate the root median square proportion deviation [RMdSPD; analogous to root median square percentage errors, see @Hyndman2006] between the true and estimated parameter values: $$RMdSPD = \sqrt{Med((\frac{\psi_{true}-\psi_{est}}{\psi_{true}})^2)}.$$
We will treat $RMdSPD < 0.1$ as good, $0.1 \le RMdSPD < 0.5$ as moderate, and $RMdSPD \ge 5$ as bad recovery of a parameter. By taking the median, we will reduce the influence of potential outliers in the estimation and using proportions will enable us to compare RMdSPD values across parameters and data sets.

@@

>>>>

For each parameter, we will calculate the root median square proportion deviation [RMdSPD; analogous to root median square percentage errors, see @Hyndman2006] between the true and estimated parameter values: $$RMdSPD = \sqrt{Med((\frac{\psi_{true}-\psi_{est}}{\psi_{true}})^2)}.$$
We will treat $RMdSPD < 0.1$ as good, $0.1 \le RMdSPD < 0.5$ as moderate, and $RMdSPD \ge 0.5$ as bad recovery of a parameter. By taking the median, we will reduce the influence of potential outliers in the estimation and using proportions will enable us to compare RMdSPD values across parameters and data sets.

@@

\newpage
